---
title: "HEALTH WORKERS SURVEY REPORT"
author: "GHID"
output:
  html_document:
    toc: yes
    toc_float:
      toc_collapsed: yes
    toc_depth: 3
    number_sections: yes
    theme: lumen
  pdf_document:
    toc: yes
    toc_depth: '3'
  word_document:
    toc: yes
    toc_depth: '3'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.height = 10,  fig.width = 14, size = 16,	message = FALSE, warning = FALSE, comment = NA)

library(tidyverse)
library(tinytex)
library(summarytools)
library(gtsummary)
library(ggstatsplot)
library(ggpubr)
library(finalfit)
library(scales)
library(ggsci)
library(httr)
library(jsonlite)
library(ftExtra)
library(janitor)

st_options(headings = F , freq.cumul = F, round.digits = 2, display.labels = F, freq.totals = F, dfSummary.valid.col = F, freq.report.nas = F, style = "rmarkdown", ctable.totals = F)
```

```{r message=FALSE, warning=FALSE, include=FALSE}
getReport <- function(x, values = "label", head="label"){
  print(x)
  df <- POST(url = 'https://redcap.ghid-kccr.org/api/',
             body = list(
               content='report',
               format='json',
               report_id= x,
               csvDelimiter='',
               rawOrLabel= values,
               token = "9C435B4AC255981BEFD49E32EB5AD2C2",
               rawOrLabelHeaders= head,
               exportCheckboxLabel='false',
               returnFormat='json'),
             encode = "form")
  content(df, as = "text") %>%
  fromJSON() %>%
    return()
}
pings <- getReport(167)
```

## FACILTY LEVEL BY GENDER
```{r message=FALSE, warning=FALSE, echo=FALSE}
pings %>% 
  select(facility_level, sex) %>% filter(sex !="") %>% filter(facility_level !="") %>% 
  remove_constant() %>% 
  tbl_cross(row = facility_level, col = sex, missing = "no", margin = "column") %>%
  bold_labels() %>% 
  modify_footnote(all_stat_cols()~"Frequency(%)") %>% 
  modify_caption("**Table 2. Response from Facility level by Sex**") %>% 
  as_flex_table()
```


## AGE DISTRIBUTION
The blue-dashed line indicates the median age of the respondents

```{r message = FALSE, warning=FALSE, echo=FALSE}
age <- as.numeric(pings$age)
pings %>% select(age) %>% 
  drop_na %>% tbl_summary()
  ggplot(aes(age)) + 
  geom_histogram(aes(y=..count..), binwidth = 5) +
  labs(title = "Graph of Age Distribution", x = "Age", y = "Count") +
  geom_vline(aes(xintercept = median(age, na.rm=T)),
             color="blue", linetype="dashed", size=1) + 
      #scale_fill_manual() +
  ggthemes::theme_clean()
```

## EDUCATION LEVEL BY GENDER

```{r message=FALSE, warning=FALSE,echo=FALSE}
pings %>% 
  select(edu, sex) %>% filter(sex !="") %>% filter(edu !="") %>% 
  tbl_cross(row = edu, 
            col = sex, 
            missing = "no", 
            margin = "column") %>% 
  bold_labels() %>% 
  modify_footnote(all_stat_cols()~"Frequency") %>% 
  modify_caption("**Table 3. Education Level by Gender**")%>% 
  as_flex_table()
```

## OCCUPATION BY FACILITY

This table shows the respondent's occupation by the facility they  work in. It is indicated that response were given by Nurses, Medical doctors, Biomedical Laboratory scientist, Public health practitioners Research scientist. and other professional health workers from Government, Faith-Based, NGO and Quasi-governmental facilities. 

```{r message=FALSE, warning=FALSE, echo=FALSE}
pings %>% select(occupation, facility) %>% filter(facility !="") %>% 
  tbl_cross(col = facility, row = occupation, missing = "no", margin = 'column') %>%
  bold_labels() %>% 
  modify_footnote(all_stat_cols()~"Frequency") %>% 
  modify_caption("**Table 1. Respondents Occupation by their Facility**") %>% 
  as_flex_table()
```

## YEARS OF WORK EXPERIENCE 
The blue-dashed line indicates the median years of work experience of the respondents

```{r message=FALSE, warning=FALSE, echo=FALSE}
pings %>% select(experience) %>% 
      drop_na %>%
      ggplot(aes(experience)) + 
      geom_histogram(aes(y=..count..), binwidth = 5) +
      labs(title = "Graph of Years of Experience", x = "Experience", y = "Count") +
      geom_vline(aes(xintercept = median(experience, na.rm=T)),
                 color="blue", linetype="dashed", size=1) +
      ggthemes::theme_clean()# +
     # scale_fill_manual(values = "green") 
```


## LOCATION BY FACILITY
The graph below shows the distribution of the location of the respondents. Each bar represents the region from which the response came and are filled with the facilities of the respondents. 


```{r message=FALSE, warning=FALSE, echo=FALSE}
pings %>% select(location, facility) %>% filter(facility !="") %>% filter(location !="") %>% 
  tbl_cross(row = location, col = facility, missing = "no", margin = 'column') %>% 
  bold_labels() %>% 
  modify_footnote(all_stat_cols()~"Frequency(%)") %>% 
  modify_caption("**Table 1. Respondents Occupation by their Facility**") %>% 
  as_flex_table()
```



## STROKE SUFFERING 

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
pings %>% 
  select(stroke, relative_stroke) %>% 
  tbl_cross(
    row = stroke,
    col = relative_stroke,
    percent = "none",
    margin = "column", 
    missing = "no") %>% 
  modify_caption("**Table 4. Respondents with stroke**") %>% 
  as_flex_table()
```

## RESPONDENTS' PERCEPTION

```{r echo=FALSE, message=FALSE, warning=FALSE}
pings %>% 
  pivot_longer(16:27, names_to = "Perception", values_to = "Response") %>% 
  mutate(
    Perception = fct_recode(Perception, 
                            "PINGS meets my Approval" = "approved",
                            "PINGS is Appealing" = "appealing",
                            "I Like PINGS" = "like",
                            "I Welcome PINGS" = "welcome",
                            "PINGS seems Fitting" = "fitting",
                            "PINGS is Suitable" = "suitable",
                            "PINGS is Applicable" = "applicable",
                            "PINGS is Good a Match" = "good_match",
                            "PINGS is Implementable"  = "implementable",
                            "PINGS is Possible" = "possible",
                            "PINGS is Doable" = "doable",
                            "PINGS seems Easy"  = "easy")
  ) %>% drop_na() %>% 
  ggplot(aes(y = Perception, fill = Response)) +
  geom_bar()+
  labs(x='Response', y = 'Perception', title = "Respondent's Response to PINGS")+
  scale_fill_manual(values = c("red1", "orange4", "snow4", "palegreen4", "green4")) +
  ggthemes::theme_clean() +
  theme(
    legend.position = "bottom"
  ) 
```

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
mdl <- glm(as.factor(facility) ~ sex + edu, data = pings, family = binomial(link = "logit"))
tbl <- tbl_regression(mdl, exponentiate = TRUE)
tbl
anova(mdl)
summary(mdl)
```

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
ping<- pings %>%
  pivot_longer(16:27,names_to = "Response", values_to = "status") %>% 
  mutate(
    Response = fct_recode(Response, 
                            "PINGS meet my Approval" = "approved",
                            "PINGS is Appealing" = "appealing",
                            "I Like PINGS" = "like",
                            "I Welcome PINGS" = "welcome",
                            "PINGS seems Fitting" = "fitting",
                            "PINGS is Suitable" = "suitable",
                            "PINGS is Applicable" = "applicable",
                            "PINGS is Good a Match" = "good_match",
                            "PINGS is Implementable"  = "implementable",
                            "PINGS is Possible" = "possible",
                            "PINGS is Doable" = "doable",
                            "PINGS seems Easy"  = "easy")
  )
ping %>% select(occupation, Response) %>% 
  tbl_summary(by = occupation) %>% 
  modify_caption("**Table 5. Respondent's Response to PINGS by their Occupation **") %>%
  as_flex_table()
```
